Error Reporting Parsers: a Monad Transformer Approach

### 2013-06-24 article.tex
Parsers: improve Parsec comparison

\Section{Parsec comparison}
A quick word about Parsec \cite{leijen}, an important, battle-tested parser 
combinator library for Haskell.

One major difference between the approach I've described and Parsec's approach
is with respect to backtracking and error-reporting.  Parsec's default is 
predictive parsing using a single token of lookahead for efficiency.  This can
be changed using its \verb+try+ combinator.

On the other hand, my approach by default uses unlimited lookahead, which can 
be modified using the \verb+throwError+ and \verb+commit+ combinators.

>>>>

\Section{Parsec comparison}
A quick word about Parsec \cite{leijen}, a popular and battle-tested parser 
combinator library for Haskell:

The approach I've described differs from Parsec's approach with respect to 
backtracking and error-reporting.  By default, Parsec generates LL(1) parsers --
this means it uses predictive parsing with only a single token of lookahead.  This
is useful for both efficiency and better error reporting.  However, often a 
single token is not enough to unambiguously determine what rule should be tried;
for these cases, one must use its \verb+try+ combinator.  It is up to the
programmer to determine when it's necessary to add \verb+try+ to a parser
implementation.

On the other hand, my approach by default uses unlimited lookahead; it also 
doesn't automatically generate meaningful errors.  It is up to the programmer 
to generate useful errors using the \verb+throwError+ and \verb+commit+ 
combinators.
